Computing solution space properties of combinatorial optimization problems via generic tensor networks

### 2022-09-02 paper/paper.tex

\section{Maximum independent sets and its counting}\label{sec:counting}
\subsection{Tropical algebra for finding the MIS size and counting MISs}
%The method we use to count the MISs is based on the following observations:
Let $x=\infty$, the independence polynomial in the previous section becomes
\begin{equation}
I(G, \infty) = \lim_{x\rightarrow \infty}\sum_{k=0}^{\alpha(G)}a_k x^k = a_{\alpha(G)} \infty^{\alpha(G)},
\end{equation}
where all terms except the one with the largest order vanish. We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type that has two fields: the largest exponent $k$ and its coefficient $a_k$.
From this, we can define a new algebra as
\begin{equation}
    \eqname{P1}
\begin{split}
    a_x\infty^x \oplus a_y\infty^y &= \begin{cases}
        (a_x + a_y)\infty^{\max(x,y)}, & x = y\\
        a_y\infty^{\max(x,y)}, & x < y\\
        a_x\infty^{\max(x,y)}, & x > y
    \end{cases}, \\
    a_x\infty^x \odot a_y\infty^y &= a_x a_y\infty^{x+y}\\
    \mymathbb{0} &= 0\infty^{-\infty}\\
    \mymathbb{1} &= 1\infty^{0}.
\end{split}%& \text{\rlap{(P1)}}
\label{eq:countingtropical}
\end{equation}
Here, we have generalized the previous polynomial to the Laurent polynomial to define the zero-element properly.
To implement this algebra programmatically, we create a data type with two fields $(x, a_x)$ to store the MIS size and its counting,
and define the above operations and constants correspondingly.
If one is only interested in finding the MIS size, one can drop the counting field.
The algebra of the exponents becomes the max-plus tropical algebra~\cite{Maclagan2015, Moore2011}:
\begin{equation}\eqname{T}
    \begin{split}
        x \oplus y &= \max(x,y)\\
        x \odot y &= x + y\\
        \mymathbb{0} &= -\infty\\
        \mymathbb{1} &= 0.
    \end{split}\label{eq:tropical}
\end{equation}
Algebra \Cref{eq:tropical} and \Cref{eq:countingtropical} are the same as those used in Liu et al.~\cite{Liu2021} to compute the spin glass ground state energy and its degeneracy.

@@

\begin{lemma}
    The number of the largest $K$ independent sets of a graph $G = (V, E)$ can be computed in time $O(K\log K)\cc$.
\end{lemma}
The proof is similar to proving \Cref{thm:complexpoly}, except only $k$ largest coefficients are involved in the addition and multiplication.

@@

\begin{theorem}\label{thm:complexset}
    The independent sets of graph $G = (V, E)$ be a graph can be enumerated in time $O(|I||V|)\cc$, where $|I|$ is the number of independent sets.
\end{theorem}
\begin{proof}
To enumerate over $I$,  we initialize variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is a basis bit string of size $|V|$ that has only one non-zero value at location $i$.
The vertex and edge tensors are thus
\begin{equation}
    \left(W^{\rm SN}\right)^{(v)} = \left(\begin{matrix}
        \mymathbb{1} \\
        \{\boldsymbol{e}_{i}\}
    \end{matrix}\right),   
    \qquad \qquad
        \left(B^{\rm SN}\right)^{(u, v)} = \left(\begin{matrix}
        \mymathbb{1}  & \mymathbb{1} \\
        \mymathbb{1} & \mymathbb{0}
    \end{matrix}\right).
\end{equation}
The contraction of this tensor network is a set with its elements being all independent set configurations. The time complexity of element-wise addition and multiplication is upper bounded by $|I||V|$, where $|V|$ comes from the linear cost of representing a $|V|$-vertex configuration. Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|I||V|)\cc$.
In practise, the huge multiplicative factor $|I|$ only appear in the last step of tensor contraction.
This complexity only upper bounds the actually performance of the algorithm.
\end{proof}

@@

\begin{theorem}\label{thm:complexmis}
    Let $G = (V, E)$ be a graph and $\mathcal{I}_\alpha$ be its maximum independent sets.
    $I_\alpha$ can be computed in time $O(|\mathcal{I}_\alpha||V|)\cc$.
\end{theorem}
\begin{proof}
By replacing the tensor elements in \Cref{sec:tnmap} with the number type defined in \Cref{eq:countingtropicalset}, with variable $x_v^{w_v} = \{\boldsymbol{e}_{v}\}\infty^{w_v}$, the vertex tensor and edge tensor become
\begin{equation}
    \left(W^{\rm P1+SN}\right)^{(v)} = \left(\begin{matrix}
        \mymathbb{1} \\
        \{\boldsymbol{e}_{v}\}\infty^{w_v}
    \end{matrix}\right),   
    \qquad \qquad
        \left(B^{\rm P1+SN}\right)^{(u, v)} = \left(\begin{matrix}
        \mymathbb{1}  & \mymathbb{1} \\
        \mymathbb{1} & \mymathbb{0}
    \end{matrix}\right).
\end{equation}
The enumeration of all MIS configurations corresponds to the contraction of this tensor network. The time complexity of element-wise addition and multiplication is upper bounded by the number of independent sets $|\mathcal{I}_\alpha|$. Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|\mathcal{I}_\alpha||V|)\cc$.
\end{proof}
However, direct contraction might have significant space overheads for keeping too many intermediate states irrelevant to the final maximum independent sets.
We introduce the bounding technique in \Cref{sec:bounding} to avoid this issue.
One may also be interested in the more studied maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} enumeration.
It will be discussed in \Cref{sec:maximal} since it requires using a different tensor network structure.

\begin{theorem}\label{thm:complexsetk}
    Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the set of independent sets with size $k$.
    The independent sets with size $k > \alpha(G)-K$ of $G$ can be computed in time $O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)\cc$.
\end{theorem}
\begin{proof}
This can proved by combining the set algebra \Cref{eq:set} with the polynomial number truncated to largest $K$ orders (\Cref{eq:max2poly}).
The number of bitstring operations in the addition and multiplication of the joint algebra is upper bounded by the elements in the sets $\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|$.
Combining with \Cref{thm:complexreal}, the overall time complexity of contracting this tensor network is $O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)\cc$.
\end{proof}

@@

\begin{corollary}
    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $O(|V|)\cc$.
\end{corollary}
The proof is similar to \Cref{thm:complexmis}, except the set algebra is replace by the one in \Cref{eq:singleconfig}, and the time complexity of element-wise addition and multiplication no longer depends on $|\mathcal{I}_\alpha|$.
The linear dependency of $|V|$ in the time complexity can be remove using the back propagation technique, at the cost of additional space.
\begin{theorem}
    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $\cc$.
\end{theorem}
\begin{proof}
    Let $\alpha(G) = \max\limits_{s \in I} \sum_{v} s_v$ be the maximum independent set size. The optimal configuration can be obtained by differentiating over vertex tensors as
    \begin{equation}
    \begin{cases}
        1, &\frac{\partial \alpha(G)}{\partial s_v} = 1\\
        0, &\frac{\partial \alpha(G)}{\partial s_v} = 0
    \end{cases}.
    \end{equation}
    It can be numerically computed by differentiating over the process of the tropical tensor network contraction, where the backward rules can be found in \Cref{sec:bounding}. The time overhead of computing single optimal solution is constant comparing to only computing the contraction. Thus the computing time complexity should be the same as in \Cref{thm:complextropical}.
\end{proof}

@@

\begin{theorem}\label{thm:complexexpr}
        The independent sets $I$ of a graph $G=(V,E)$ can be enumerated in time $\cc + O(|V||I|)$.
\end{theorem}
\begin{proof}
By replacing the tensor elements with the number type in \Cref{eq:expr} with $x_v^{w_v}$ mapped to $(\texttt{LEAF},\boldsymbol{e}_i,/,/)$, the vertex tensor and edge tensor become
\begin{equation}
    \left(W^{\rm EXPR}\right)^{(v)} = \left(\begin{matrix}
        \mymathbb{1} \\
        (\texttt{LEAF},\boldsymbol{e}_i,/,/)
    \end{matrix}\right),   
    \qquad
        \left(B^{\rm EXPR}\right)^{(u, v)} = \left(\begin{matrix}
        \mymathbb{1}  & \mymathbb{1} \\
        \mymathbb{1} & \mymathbb{0}
    \end{matrix}\right).
\end{equation}
The contraction of such tensor network corresponds to a sum-product expression tree of the set of independent sets, which costs time $\cc$ by \Cref{thm:complexreal} since the computing time of expression tree addition and multiplication are $O(1)$.
The time complexity to evaluating this expression tree is $O(|V||I|)$, where $|V|$ comes from the number of bits to represent a configuration.
\end{proof}

Similarly, we have the following lemma by combining the sum-product expression tree algebra with the truncated polynomial.

\begin{lemma}\label{thm:complexexprk}
        Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the number of independent sets with size $k$. The independent sets with size $k > \alpha(G)-K$ of can be computed in time $O(K\log K)\cc + O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)$.
\end{lemma}

Although likely, one cannot collect all configurations represented by a sum-product expression tree into a vector due to its extremely large size,
they can draw unbiased samples from it by direct sampling.
\begin{theorem}
    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $\cc + O(|V|^2 M)$, where $M$ is the number of samples.
\end{theorem}
\begin{proof}
Similar to the proof of \Cref{thm:complexexpr}, we first obtain a sum-product tree representation of the configurations in time $\cc$.
Then we show to generate a sample, the cost is $O(|V|^2)$.
The sampling program starts from the root node and descends this tree recursively to the left and right siblings.
If a node has type \texttt{SUM}, the program draws samples from the left and right siblings with a probability decided by the size of each sub-tree and returns the union of samples.
Otherwise, if a node has type \texttt{PROD}, the program draws two sets of samples of equal sizes from its left and right siblings and returns the element-wise multiplication ($\lor^\circ$) of them.
The recursion stops at a \texttt{LEAF} node having size $1$ or a \texttt{ZERO} node having size $0$.
In a sum-product expression tree, the number of configurations of sub-trees can be determined easily as we will show in the following example.
\begin{example}
Let us consider the following sum-product expression tree 
\begin{equation*}
    (\texttt{SUM}, /, (\texttt{PROD}, /, A, B), (\texttt{SUM}, /, C, D)),
\end{equation*}
where sub-trees $A, B, C$ and $D$ can be any of the four types of nodes.
This sum-product expression tree can be represented diagrammatically as the following:

@@

Since the depth of the expression tree is $|V|$ and the cost of each arithmetic operation is $O(|V|)$, the overall time complexity to generate a sample is $O(|V|^2)$.
\end{proof}

Similarly, if one is only interested in obtaining independent sets with largest $K$ sizes, we have the following lemma.
\begin{lemma}
    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(K\log K)\cc + O(|V|^2 M)$, where $M$ is the number of samples.
\end{lemma}

@@

\begin{lemma}
    Let $G = (V, E, W)$ be a weighted graph, its $K$ largest independent sets can be computed in time $O(K\log K|V|)\cc$.
\end{lemma}
To find solutions corresponding to the largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Cref{eq:singleconfig}).
Since the $\oplus$ operation of the configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.

>>>>

\section{Maximum independent sets and its counting}\label{sec:counting}
\subsection{The number of independent sets}
\begin{theorem}\label{thm:complexrealnum}
    Let $G = (V, E)$ be a graph, the total number independent sets of $G$ can be computed in time $\cc$.
\end{theorem}
\begin{proof}
Let $x = 1$ be a real constant number, the independence polynomial in the previous section becomes
\begin{equation}
I(G, 1) = \sum_{k=0}^{\alpha(G)}a_k,
\end{equation}
which corresponds to the total number of independent sets.
Since the real number addtion and multiplication can be computed in $O(1)$ time,
proving the theorem by \Cref{thm:complexreal}.
\end{proof}

\subsection{Tropical algebra for finding the MIS size and counting MISs}
%The method we use to count the MISs is based on the following observations:
Let $x=\infty$, the independence polynomial in the previous section becomes
\begin{equation}
I(G, \infty) = \lim_{x\rightarrow \infty}\sum_{k=0}^{\alpha(G)}a_k x^k = a_{\alpha(G)} \infty^{\alpha(G)},
\end{equation}
where all terms except the one with the largest order vanish. We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type that has two fields: the largest exponent $k$ and its coefficient $a_k$.
From this, we can define a new algebra as
\begin{equation}
    \eqname{P1}
\begin{split}
    a_x\infty^x \oplus a_y\infty^y &= \begin{cases}
        (a_x + a_y)\infty^{\max(x,y)}, & x = y\\
        a_y\infty^{\max(x,y)}, & x < y\\
        a_x\infty^{\max(x,y)}, & x > y
    \end{cases}, \\
    a_x\infty^x \odot a_y\infty^y &= a_x a_y\infty^{x+y}\\
    \mymathbb{0} &= 0\infty^{-\infty}\\
    \mymathbb{1} &= 1\infty^{0}.
\end{split}%& \text{\rlap{(P1)}}
\label{eq:countingtropical}
\end{equation}
Here, we have generalized the previous polynomial to the Laurent polynomial to define the zero-element properly.
To implement this algebra programmatically, we create a data type with two fields $(x, a_x)$ to store the MIS size and its counting,
and define the above operations and constants correspondingly.
If one is only interested in finding the MIS size, one can drop the counting field.
The algebra of the exponents becomes the max-plus tropical algebra~\cite{Maclagan2015, Moore2011}:
\begin{equation}\eqname{T}
    \begin{split}
        x \oplus y &= \max(x,y)\\
        x \odot y &= x + y\\
        \mymathbb{0} &= -\infty\\
        \mymathbb{1} &= 0.
    \end{split}\label{eq:tropical}
\end{equation}
Algebra \Cref{eq:tropical} and \Cref{eq:countingtropical} are the same as those used in Liu et al.~\cite{Liu2021} to compute the spin glass ground state energy and its degeneracy.

@@

\begin{theorem}
    The number of the largest $K$ independent sets of a graph $G = (V, E)$ can be computed in time $O(K\log K)\cc$.
\end{theorem}
The proof is similar to proving \Cref{thm:complexpoly}, except only $k$ largest coefficients are involved in the addition and multiplication.

@@

\begin{lemma}\label{thm:complexset}
    The independent sets of graph $G = (V, E)$ be a graph can be enumerated in time $O(|I||V|)\cc$, where $|I|$ is the number of independent sets.
\end{lemma}
\begin{proof}
To enumerate over $I$,  we initialize variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is a basis bit string of size $|V|$ that has only one non-zero value at location $i$.
The vertex and edge tensors are thus
\begin{equation}
    \left(W^{\rm SN}\right)^{(v)} = \left(\begin{matrix}
        \mymathbb{1} \\
        \{\boldsymbol{e}_{i}\}
    \end{matrix}\right),   
    \qquad \qquad
        \left(B^{\rm SN}\right)^{(u, v)} = \left(\begin{matrix}
        \mymathbb{1}  & \mymathbb{1} \\
        \mymathbb{1} & \mymathbb{0}
    \end{matrix}\right).
\end{equation}
The contraction of this tensor network is a set with its elements being all independent set configurations. The time complexity of element-wise addition and multiplication is upper bounded by $|I||V|$, where $|V|$ comes from the linear cost of representing a $|V|$-vertex configuration. Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|I||V|)\cc$.
In practise, the huge multiplicative factor $|I|$ only appear in the last step of tensor contraction.
This complexity only upper bounds the actually performance of the algorithm.
\end{proof}

@@

\begin{lemma}\label{thm:complexmis}
    Let $G = (V, E)$ be a graph and $\mathcal{I}_\alpha$ be its maximum independent sets.
    $I_\alpha$ can be computed in time $O(|\mathcal{I}_\alpha||V|)\cc$.
\end{lemma}
\begin{proof}
By replacing the tensor elements in \Cref{sec:tnmap} with the number type defined in \Cref{eq:countingtropicalset}, with variable $x_v^{w_v} = \{\boldsymbol{e}_{v}\}\infty^{w_v}$, the vertex tensor and edge tensor become
\begin{equation}
    \left(W^{\rm P1+SN}\right)^{(v)} = \left(\begin{matrix}
        \mymathbb{1} \\
        \{\boldsymbol{e}_{v}\}\infty^{w_v}
    \end{matrix}\right),   
    \qquad \qquad
        \left(B^{\rm P1+SN}\right)^{(u, v)} = \left(\begin{matrix}
        \mymathbb{1}  & \mymathbb{1} \\
        \mymathbb{1} & \mymathbb{0}
    \end{matrix}\right).
\end{equation}
The enumeration of all MIS configurations corresponds to the contraction of this tensor network. The time complexity of element-wise addition and multiplication is upper bounded by the number of independent sets $|\mathcal{I}_\alpha|$. Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|\mathcal{I}_\alpha||V|)\cc$.
\end{proof}
However, direct contraction might have significant space overheads for keeping too many intermediate states irrelevant to the final maximum independent sets.
We introduce the bounding technique in \Cref{sec:bounding} to avoid this issue.
One may also be interested in the more studied maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} enumeration.
It will be discussed in \Cref{sec:maximal} since it requires using a different tensor network structure.

\begin{lemma}\label{thm:complexsetk}
    Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the set of independent sets with size $k$.
    The independent sets with size $k > \alpha(G)-K$ of $G$ can be computed in time $O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)\cc$.
\end{lemma}
\begin{proof}
This can proved by combining the set algebra \Cref{eq:set} with the polynomial number truncated to largest $K$ orders (\Cref{eq:max2poly}).
The number of bitstring operations in the addition and multiplication of the joint algebra is upper bounded by the elements in the sets $\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|$.
Combining with \Cref{thm:complexreal}, the overall time complexity of contracting this tensor network is $O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)\cc$.
\end{proof}

@@

\begin{proposition}
    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $O(|V|)\cc$.
\end{proposition}
The proof is similar to \Cref{thm:complexmis}, except the set algebra is replace by the one in \Cref{eq:singleconfig}, and the time complexity of element-wise addition and multiplication no longer depends on $|\mathcal{I}_\alpha|$.
The linear dependency of $|V|$ in the time complexity can be remove using the back propagation technique, at the cost of additional space.
\begin{theorem}
    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $\cc$.
\end{theorem}
\begin{proof}
    Let $\alpha(G) = \max\limits_{s \in I} \sum_{v} s_v$ be the maximum independent set size. The optimal configuration can be obtained by differentiating over vertex tensors as
    \begin{equation}
    \begin{cases}
        1, &\frac{\partial \alpha(G)}{\partial s_v} = 1\\
        0, &\frac{\partial \alpha(G)}{\partial s_v} = 0
    \end{cases}.
    \end{equation}
    It can be numerically computed by differentiating over the process of the tropical tensor network contraction, where the backward rules can be found in \Cref{sec:bounding}. The time overhead of computing single optimal solution is constant comparing to only computing the contraction. Thus the computing time complexity should be the same as in \Cref{thm:complextropical}.
\end{proof}

@@

\begin{theorem}\label{thm:complexexpr}
        The independent sets $I$ of a graph $G=(V,E)$ can be enumerated in time $\cc + O(|V||I|)$.
\end{theorem}
\begin{proof}
By replacing the tensor elements with the number type in \Cref{eq:expr} with $x_v^{w_v}$ mapped to $(\texttt{LEAF},\boldsymbol{e}_i,/,/)$, the vertex tensor and edge tensor become
\begin{equation}
    \left(W^{\rm EXPR}\right)^{(v)} = \left(\begin{matrix}
        \mymathbb{1} \\
        (\texttt{LEAF},\boldsymbol{e}_i,/,/)
    \end{matrix}\right),   
    \qquad
        \left(B^{\rm EXPR}\right)^{(u, v)} = \left(\begin{matrix}
        \mymathbb{1}  & \mymathbb{1} \\
        \mymathbb{1} & \mymathbb{0}
    \end{matrix}\right).
\end{equation}
The contraction result of this tensor network corresponds to a sum-product expression tree for the set of independent sets.
Unlike in \Cref{thm:complexset}, the contraction complexity is independent of the set size, i.e. the time complexity is $\cc$ by \Cref{thm:complexreal}.
The time complexity to evaluating this expression tree is $O(|V||I|)$, where $|V|$ comes from the number of bits to represent a configuration.
Proving the theorem by adding two computing times.
\end{proof}

Similarly, we have the following corollary by combining the sum-product expression tree algebra with the truncated polynomial.

\begin{corollary}\label{thm:complexexprk}
        Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the number of independent sets with size $k$. The independent sets with size $k > \alpha(G)-K$ of can be computed in time $O(K\log K)\cc + O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)$.
\end{corollary}
Again, the theorem can be proved by relating it with its set algebra version in \Cref{thm:complexsetk}. Although likely, one cannot collect all configurations represented by a sum-product expression tree into a vector due to its extremely large configuration space,
one can draw samples unbiasedly from it by direct sampling.
\begin{theorem}
    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $\cc + O(|V|^2 M)$, where $M$ is the number of samples.
\end{theorem}
\begin{proof}
Similar to the proof of \Cref{thm:complexexpr}, we first obtain a sum-product tree representation of the configurations in time $\cc$.
Then we show to generate a sample, the cost is $O(|V|^2)$.
The sampling program starts from the root node and descends this tree recursively to the left and right siblings.
If a node has type \texttt{SUM}, the program draws samples from the left and right siblings with a probability decided by the size of each sub-tree and returns the union of samples.
Otherwise, if a node has type \texttt{PROD}, the program draws two sets of samples of equal sizes from its left and right siblings and returns the element-wise multiplication ($\lor^\circ$) of them.
The recursion stops at a \texttt{LEAF} node having size $1$ or a \texttt{ZERO} node having size $0$.
In a sum-product expression tree, the number of configurations of sub-trees can be determined easily as we will show in the following example.
\begin{example}
Let us consider the following sum-product expression tree 
\begin{equation*}
    (\texttt{SUM}, /, (\texttt{PROD}, /, A, B), (\texttt{SUM}, /, C, D)),
\end{equation*}
where sub-trees $A, B, C$ and $D$ can be any of the four types of nodes.
This sum-product expression tree can be represented diagrammatically as the following:

@@

Since the depth of the expression tree is $O(|V|)$ and the cost of each arithmetic operation is also $O(|V|)$, the overall time complexity to generate a sample is $O(|V|^2)$.
Proving the theorem.
\end{proof}

Similarly, if one is only interested in obtaining independent sets with largest $K$ sizes, we have the following corollary.
\begin{corollary}
    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(K\log K)\cc + O(|V|^2 M)$, where $M$ is the number of samples.
\end{corollary}

@@

\begin{corollary}
    Let $G = (V, E)$ be a weighted graph, its $K$ largest independent sets can be computed in time $O(K\log K|V|)\cc$.
\end{corollary}
To find solutions corresponding to the largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Cref{eq:singleconfig}).
Since the $\oplus$ operation of the configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.
